Supplementary Methods for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-11-19 Documents/supplementary_information.tex
Tweaked a bit.

@@

Our model has 8 HIV states (Extended Data Fig.~\ref*{model_diag}):
susceptible to HIV infection ($S$ is the number of people
susceptible), vaccinated against HIV ($R$), acute HIV infection ($A$),
undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
($D$), treated without viral suppression ($T$), viral suppression
($V$), and having AIDS ($W$).  Viral suppression is defined as a viral
load of less than 1000 viral RNA copies per mL of blood.  Viral
suppression not only extends survival but also dramatically reduces
transmission
\autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.

@@

The parametrized differential equations were solved numerically using
the LSODA routine \autocite{odepack, scipy, medlock2016-git} and four
effectiveness outcomes were computed from the solutions.
\begin{description}
\item[New infections] New infections from 2015 to time $t$ are given
  by $Y(t)$.

>>>>

We developed a country-level mathematical model of HIV transmission
and progression that stratifies HIV infection into acute, chronic
undiagnosed, chronic diagnosed, chronic treated, chronic virally
suppressed, and AIDS, along with uninfected unvaccinated and
vaccinated people (\autoref{model} \&
\hyperref[model_diag]{Extended Data Fig.~\ref*{model_diag}}).
Simulations of our country-level model project the number of people in
each HIV stratum from 2015 to 2035, from which statistics such as
prevalence and incidence were calculated.  Model transition rates were
adjusted dynamically to meet intervention goals for diagnosis,
treatment, viral suppression, and vaccination coverage
(\autoref{targets}).  Data and estimates from many sources were used
to parametrize the model (\autoref{data_sources}).  Country-specific
transmission rates were fitted to historical estimates of the
trajectories of incidence and prevalence, spanning from as early as
1990 for some countries (\autoref{model_fitting}). For every scenario
of intervention combinations, we conducted 1000 model simulations,
sampling values of model parameters from empirical distributions for
each simulation, and summarized the results with median and
percentiles (\autoref{uncertainty}).

@@

Our model has 8 HIV states (Extended Data Fig.~\ref*{model_diag}):
susceptible to HIV infection ($S$ is the number of people
susceptible), vaccinated against HIV ($R$), acute HIV infection ($A$),
undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
($D$), treated without viral suppression ($T$), viral suppression
($V$), and having AIDS ($W$).  Viral suppression is defined as a viral
load of less than 1000 viral RNA copies per mL of blood.  Viral
suppression not only extends survival but also dramatically reduces
transmission
\autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
Simulations of our model project the number of people in each HIV
stratum from 2015 to 2035.

@@

The parametrized differential equations were solved numerically from
year 2015 to year 2035 using the LSODA routine
\autocite{odepack, scipy, medlock2016-git} and four effectiveness
outcomes were computed from the solutions.
\begin{description}
\item[New infections] New infections from 2015 to time $t$ are given
  by $Y(t)$.
